\documentclass[11pt,a4paper]{article}
\usepackage[english]{babel}
\input{cover-letter-style.tex}

\begin{document}

Gowago AG\\
Josefstrasse 216\\
8005 Zurich

\vspace{12pt}

Zurich, January 27, 2026

\vspace{12pt}

\textbf{Application for Senior Software Engineer (Backend focused)}

\vspace{6pt}

Dear Filipe Abrahao,

Gowago excites me as a digital platform that makes mobility simple, transparent, and customer-friendly. I am particularly drawn to the combination of product, data, and engineering to create a seamless customer experience across the entire lifecycle. I would like to bring my experience in building and operating data-driven applications to help scale the platform and continuously improve the user experience.

Having worked in the car industry at AutoForm and in the fintech sector at Yokoy, I am excited that Gowago sits at the intersection of car leasing and payments. I bring relevant industry experience across mobility and payments to the role.

In my current role as a software engineer in the financial sector, I develop robust, high performance services with a focus on scalability, observability, and automated testing. I work closely with product and data teams, optimize database queries, and reliably ship distributed services into production. A key focus of my work is automating development and operations processes, which has improved system stability and reduced incident resolution times. These experiences translate directly to evolving a high-growth platform like Gowago. I already contribute occasional frontend work and enjoy supporting the team there when it adds value.

With a master's degree in Computational Science and Engineering from ETH Zurich and experience with data-driven backends, relational databases, and cloud-adjacent operations, I can onboard quickly and pragmatically improve complex systems. As a French-Swiss dual citizen with German and French as native languages and excellent English skills, I am also linguistically flexible for an interdisciplinary environment.

I would welcome the opportunity to discuss how my technical background and hands-on mindset can contribute to Gowago's mission.

\vspace{12pt}

Kind regards

\vspace{18pt}

Marc Maetz

\end{document}
