\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[german]{babel}
\usepackage{setspace}
\usepackage{fancyhdr}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\pagenumbering{gobble}
\setlength{\headheight}{14pt}

\newcommand{\contactline}{%
  {\fontsize{10}{12}\selectfont
  Marc Maetz \textbar{} Langfurren 32 \textbar{} 8057 Zürich \textbar{} marc.maetz@proton.me \textbar{} +41 77 434 15 25}%
}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\contactline}
\fancyfoot[C]{\contactline}

\begin{document}

Siemens Digital Industries Software\\
z.H. Hiring Manager\\
(Online Application Portal)

\vspace{12pt}

Zürich, \today

\vspace{12pt}

\textbf{Application for Software Engineer -- Maths \& Systems (Job ID: 490660)}

\vspace{12pt}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer -- Maths \& Systems position at Siemens Digital Industries Software, as advertised on your careers portal. With a Master of Science in Computational Science and Engineering and a Bachelor’s in Physics from ETH Zürich, I possess the deep technical foundation in mathematics and simulation required to contribute to the integration of Simcenter Compose across the Siemens ecosystem.

My background uniquely aligns with the core requirements of this role:

\begin{itemize}
  \item \textbf{Strong C/C++ and Algorithmic Expertise:} During my four years at AutoForm, I developed performance-critical C-algorithms for simulation workloads, specifically focused on optimizing memory and computational efficiency. This experience working within large, complex codebases directly supports your requirement for high-quality code and robust simulation features.
  \item \textbf{Bridge Between Scripting and Systems:} I have extensive experience with Python and MATLAB, which are central to Simcenter Compose. At KIER, I utilized MATLAB for solar concentrator simulations, and in my current role as a Software Engineer, I leverage Python for high-throughput systems. I am highly comfortable developing integrations between interpreted languages and core C/C++ architectures.
  \item \textbf{API Design and Systems Interoperability:} My recent work involves designing and operating secure REST-integrations and managing complex data pipelines. I am eager to apply this expertise to develop new Compose toolboxes and ensure seamless interoperability between Siemens applications.
  \item \textbf{Reliability and Testing:} I have a proven track record of implementing automated tests, monitoring, and regression testing to ensure the high availability and reliability of production systems.
\end{itemize}

I am particularly drawn to Siemens because of its leadership in industrial software and the opportunity to work on tools that empower engineers to design everything from Formula 1 cars to space exploration vehicles. My dual-language proficiency in German and French, along with C1-level English, allows me to collaborate effectively within your global R\&D teams.

Thank you for your time and consideration. I look forward to the possibility of discussing how my technical skills in simulation and systems engineering can support the growth of Simcenter Compose.

\vspace{12pt}

Sincerely,

\vspace{18pt}

Marc Maetz

\end{document}
