\documentclass[a4paper,11pt]{article}

\usepackage[margin=1.8cm]{geometry}
\usepackage{tikz}
\usetikzlibrary{shadows}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\pagestyle{empty}
\usepackage[default]{lato}


\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt}

\definecolor{accent}{HTML}{1F4E79}
\definecolor{textgray}{gray}{0.25}
\definecolor{boxyellow}{HTML}{FFF176}

% Title box: yellow border, no fill, black text, full column width
\newcommand{\boxedtitle}[1]{%
  \tikz[baseline=(t.base)]{
    \node[
      draw=boxyellow,
      fill=white,   % was: fill=none
      text=black,
      line width=2pt,
      inner xsep=6pt,
      inner ysep=4pt,
      rounded corners=2pt,
      text width=\linewidth,
      align=left,
      drop shadow={shadow xshift=2pt, shadow yshift=-2pt, fill=black!25}
    ] (t) {\bfseries #1};
  }%
}

% Content box: black border, no fill, gray text, auto height
\newcommand{\boxedcontent}[1]{%
  \tikz[baseline=(c.base)]{
    \node[
      draw=black,
      fill=white,   % was: fill=none
      text=textgray,
      line width=1pt,
      inner xsep=6pt,
      inner ysep=6pt,
      rounded corners=2pt,
      text width=\linewidth,
      align=left,
      drop shadow={shadow xshift=2pt, shadow yshift=-2pt, fill=black!25}
    ] (c) {#1};
  }%
}

\begin{document}

% --- Right sidebar background with TikZ (only decoration) ---
\begin{tikzpicture}[remember picture,overlay]
  \fill[accent!5]
    (current page.north east)
    rectangle ++(-0.385\paperwidth,-\paperheight);
\end{tikzpicture}

% --- Header (normal LaTeX) ---
{\LARGE\bfseries Marc Maetz}\\[2pt]
{\large Software Engineer}

\vspace{0.8cm}

% --- Two-column layout with minipages ---
\noindent
\begin{minipage}[t]{0.60\textwidth}
  \raggedright

  \boxedtitle{Skills}\\[2pt]
  \boxedcontent{%
    NodeJS, TypeScript, Express\\
    C, C\texttt{++}, Java, Python, R\\
    Google Cloud Platform (GCP)\\
    Microservices, APIs, Databases\\
    Performance optimisation\\
    Complex algorithms\\
    Linux\\
    High-performance computing
  }

  \vspace{0.7cm}

  \boxedtitle{Experience}\\[2pt]
  \boxedcontent{%
    \textbf{Backend Software Engineer (TypeScript, Python)}\\
    Yokoy \textbar\ Finance \hfill 2022--now, Zurich (CH)\\[-1pt]
    \begin{itemize}
      \item Scaled a microservice backend for a smart card payment platform by an order of magnitude.
      \item Developed internal tooling to speed up incident investigation and resolution.
      \item Worked in a fast-paced agile team with cross-functional collaboration.
      \item Took ownership of complex problems from initial framing to solution.
    \end{itemize}

    \vspace{4pt}
    \textbf{Software Engineer (C)}\\
    AutoForm \textbar\ Mechanical engineering \hfill 2018--2022, Zurich (CH)\\[-1pt]
    \begin{itemize}
      \item Implemented performance-critical algorithms for sheet metal forming simulations.
      \item Focused on numerical robustness and computational efficiency.
    \end{itemize}

    \vspace{4pt}
    \textbf{Software Developer (Java)}\\
    Unitek Engineering \textbar\ Finance \hfill 2017--2018, Zurich (CH)\\[-1pt]
    \begin{itemize}
      \item Built adapters to integrate and expose external fund information.
    \end{itemize}

    \vspace{4pt}
    \textbf{R\&D Intern (MATLAB)}\\
    KIER \textbar\ Mechanical engineering \hfill 2014, Daejeon (KR)\\[-1pt]
    \begin{itemize}
      \item Contributed to simulation and analysis for solar concentrator research.
    \end{itemize}
  }

\end{minipage}%
\hfill
\begin{minipage}[t]{0.35\textwidth}
  \raggedright

  \boxedtitle{Contact}\\[2pt]
  \boxedcontent{%
    marc.maetz@proton.me\\
    +41 77 434 15 25\\
    Zurich, Switzerland\\
    Swiss and French citizen\\
    \href{https://linkedin.com/in/marc-maetz}{linkedin.com/in/marc-maetz}
  }

  \vspace{0.7cm}

  \boxedtitle{Languages}\\[2pt]
  \boxedcontent{%
    German (native)\\
    French (native)\\
    English (fluent)
  }

  \vspace{0.7cm}

  \boxedtitle{Education}\\[2pt]
  \boxedcontent{%
    ETH Zurich, Master of Science\\
    Computational Science and \\Engineering
  } \\ \vspace{0.1cm}

    \boxedcontent{%
    ETH Zurich, 
    Bachelor of Science\\
    Physics
  }
  \\
  \vspace{0.1cm}
    \boxedcontent{%
    KTH Royal Institute of Technology, Stockholm\\
    Exchange semester
  }

  \vspace{0.7cm}

  \boxedtitle{Beyond work}\\[2pt]
  \boxedcontent{%
    Amateur theatre\\
    Running, cycling\\
    Gym\\
    Climbing, mountaineering
  }

\end{minipage}

\end{document}

